% Dr. Geoff Boeing - Curriculum Vitae
% Copyright 2020 Geoff Boeing
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{zh_CN-Adobefonts_external}

% what is your name?
\newcommand{\myname}{闫增强}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
	left=1.0in,
	top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
			\setlength{\parskip}{0em}
			\setlength{\itemsep}{\listitemspace}
			\setlength{\parsep}{\listitemspace}}}
	{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
	labelindent=0em,
	topsep=0em,
	partopsep=0em,
	itemsep=\listitemspace,
	parsep=\listitemspace,
	font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
	colorlinks  = true,
	urlcolor    = black,
	pdfauthor   = {\myname},
	pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
	pdftitle    = {\myname: Curriculum Vitae},
	pdfsubject  = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\begin{document}
	\raggedright
	
	% display name as the document title
	\namefont{\myname}
	
	% contact info
	\vspace{1em}
	\begin{minipage}[t]{0.6\textwidth}
		\textbf{Post-Doctoral Fellow}\\
		Department of Computer Science and Engineering \\
		Hong Kong University of Science and Technology
		%\\Los Angeles, California, USA
	\end{minipage}
	\begin{minipage}[t]{0.39\textwidth}
		Email: \href{mailto:z.yan@connect.ust.hk}{z.yan@connect.ust.hk} \\
		Phone: +852 6153 1250 \\
		Web: \href{http://www.cse.ust.hk/~zyanad/}{http://www.cse.ust.hk/~zyanad/}
	\end{minipage}
	\vspace{0.5em}
	
	
	
	\section{Education}
	
	\begin{tablist}
		
		\item[Ph.D.] \tab Computer Science and Engineering, Hong Kong University of Science and Technology, 2020
		
		\item[M.S.]  \tab Information Engineering, Huazhong University of Science and Technology, China, 2016
		
		\item[B.S.]  \tab Information Engineering, Huazhong University of Science and Technology, China, 2013
		
	\end{tablist}
	
	
	
	\section*{Academic Appointments}
	
	\begin{tablist}
		
		\item[2020.09 - present]   \tab Hong Kong University of Science and Technology \\
		\tab Postdoctoral Research Fellow, Department of Computer Science and Engineering
		
	\end{tablist}
	
	
	
	\section*{Research Areas}
	
	\begin{itemize}
		
		\item Deep learning: domain adaptation, federated learning
		
		\item Medical imaging: retinal vessel segmentation, gland instance segmentation, prostate cancer detection
		
	\end{itemize}
	
	\section*{Selected Publications}
	
	\href{https://scholar.google.com.hk/citations?hl=zh-CN&user=j0-TqGAAAAAJ&view_op=list_works}{[Full Publications]}
	
	\subsection*{Under Review/Submission}
	
	\begin{tablist}
		
		\item[2020] \tab \textbf{Z. Yan}, J. Wicaksana, Shichao Li, X. Yang, and K. -T. Cheng. \enquote{Cycle\textsuperscript{2}GAN: Weakly Supervised Image-to-Image Translation for Medical Image Data.} preparing for \textit{IEEE Transactions on Medical Imaging}.
		
		\item[2020] \tab \textbf{Z. Yan}, J. Wicaksana, Shichao Li, and K. -T. Cheng. \enquote{Weakly Supervised Domain Adaptation for Tumor Segmentation in Breast Ultrasound Images.} preparing for \textit{IEEE Transactions on Medical Imaging}.
		
		\item[2020] \tab Shichao Li, \textbf{Z. Yan}, Hongyang Li, and K. -T. Cheng. \enquote{Exploring Intermediate Representation for Monocular Vehicle Pose Estimation.} submitted to \textit{CVPR}.
		
	\end{tablist}
		
	\subsection*{Articles in Peer-Reviewed Journals}
	
	\begin{tablist}
		
		\item[2020] \tab \textbf{Z. Yan}, J. Wicaksana, Z. Wang, X. Yang, and K. -T. Cheng. \enquote{Variation-Aware Federated Learning with Multi-Source Decentralized Medical Image Data.} \textit{IEEE Journal of Biomedical and Health Informatics}, in press.
		
		\item[2020] \tab \textbf{Z. Yan}, X. Yang, and K. -T. Cheng. \enquote{Enabling a Single Deep Learning Model for Accurate Gland Instance Segmentation: A Shape-Aware Adversarial Learning Framework.} \textit{IEEE Transactions on Medical Imaging}, 39 (6), 2176-2189, 2020.
		
		\item[2019] \tab \textbf{Z. Yan}, X. Yang, and K. -T. Cheng. \enquote{A Three-Stage Deep Learning Model for Accurate Retinal Vessel Segmentation.}  \textit{IEEE Journal of Biomedical and Health Informatics}, 23 (4), 1427-1436, 2019. \textbf{ESI Highly Cited Paper}
		
		\item[2018] \tab \textbf{Z. Yan}, X. Yang, and K. -T. Cheng. \enquote{Joint Segment-Level and Pixel-Wise Losses for Deep Learning based Retinal Vessel Segmentation.} \textit{IEEE Transactions on Biomedical Engineering}, 65 (9), 1912-1923, 2018.
		
		\item[2018] \tab \textbf{Z. Yan}, X. Yang, and K. -T. Cheng. \enquote{A Skeletal Similarity Metric for Quality Evaluation of Vessel Segmentation.} \textit{IEEE Transactions on Medical Imaging}, 37 (4), 1045-1057, 2018.
		
		\item[2018] \tab K. Ikeuchi, Z. Ma, \textbf{Z. Yan}, S. Kudoh, and M. Nakamura. \enquote{Describing Upper Body Motions based on the Labanotation for Learning-from-Observation Robots.} \textit{International Journal of Computer Vision}, 126 (12), 1415-1429, 2018.
		
%		\item[2017] \tab H. Deng, J. Wu, L. Zhu, \textbf{Z. Yan}, and L. Yu. \enquote{Texture Edge-Guided Depth Recovery for Structured Light-based Depth Sensor.} \textit{Multimedia Tools and Applications}, 76 (3), 4211-4226, 2017.
%		
%		\item[2017] \tab C. Zhu, L. Yu, \textbf{Z. Yan},and S. Xiang. \enquote{Frequency Estimation of the Plenoptic Function Using the Autocorrelation Theorem.} \textit{IEEE Transactions on Computational Imaging}, 3 (4), 1045-1057, 2017.
%		
%		\item[2014] \tab \textbf{Z. Yan}, L. Yu, Y. Yang, and Q. Liu. \enquote{Beyond the Interference Problem: Hierarchical Patterns for Multiple-Projector Structured Light System.} \textit{Applied Optics}, 53 (17), 3621-3632, 2014.
		
	\end{tablist}

	
	
	\subsection*{Conference Proceedings}
	
	\begin{tablist}
		
		\item[2018] \tab \textbf{Z. Yan}, X. Yang, and K. -T. Cheng. \enquote{A Deep Model with Shape-Preserving Loss for Gland Instance Segmentation.} \textit{International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI)}, pp. 138-146, 2018.
		
%		\item[2015] \tab \textbf{Z. Yan}, L. Yu, and Z. Xiong. \enquote{Texture-Free Large-Area Depth Recovery for Planar Surfaces.} \textit{IEEE 17th International Workshop on Multimedia Signal Processing (MMSP)}, pp. 1-6, 2015.
%		
%		\item[2015] \tab \textbf{Z. Yan}, L. Yu, and Z. Xiong. \enquote{Large-Area Depth Recovery for RGB-D Camera.} \textit{IEEE International Conference on Image Processing (ICIP)}, pp. 1409-1413, 2015.
		
	\end{tablist}


	
	\section*{Awards and Honors}
	
	\begin{tablist}
		
		\item[2015] \tab Top 10\% Paper Award, IEEE MMSP
		
		\item[2015] \tab Travel Award, IEEE ICIP
		
	\end{tablist}
	
	
	
	\section*{Service}
	
	\subsection*{Academic Journal Peer Review}
	
	\begin{itemize}
		
		\item \textit{IEEE Journal of Biomedical and Health Informatics}
		\item \textit{IEEE Transactions on Medical Imaging}
		\item \textit{IEEE Transactions on Cybernetics}
		
	\end{itemize}
	
	\subsection*{Academic Conference Peer Review}
	
	\begin{itemize}
		
		\item \textit{MICCAI}
		
	\end{itemize}
	
	% display today's date as Month Year after a vertical space below the end of the text
	\begin{center}
		%\vspace{6em}
		\vfill
		Updated \monthyeardate\today
	\end{center}
	
	
\end{document}